What the hell is the title of this paper?

### 2018-05-13 NIPS 2018/main.tex
New figures

In this section, we provide an experimental evaluation of our approach. We begin by analyzing the behavior of our algorithm on a toy problem in Sec. \ref{sec:gw}. Then, in Sec. \ref{sec:cc}, we consider two classic control benchmarks, namely cartpole and mountain car. We conclude with a complex maze navigation task in Sec. \ref{sec:mn}. In all experiments, we compare the behavior of our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT). To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective. \todo{Any better motivation?}

@@

\begin{figure*}[t]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.5cm]{images/rooms.pdf} \hfill
\includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
\caption{Bla bla bla}
    \label{fig:puddleworld}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room-gen/lrev.pdf} \hfill
\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
\caption{Bla bla bla}
    \label{fig:acrobot}
\end{minipage}
\end{figure*}

>>>>

In this section, we provide an experimental evaluation of our approach. We begin by analyzing the behavior of our algorithm on a toy problem in Sec. \ref{sec:gw}. Then, in Sec. \ref{sec:cc}, we consider two classic control benchmarks, namely cartpole and mountain car. We conclude with a complex maze navigation task in Sec. \ref{sec:mn}. In all experiments, we compare our variational transfer algorithm with Gaussian distributions (GVT) and with mixture of Gaussians (MGVT) to plain no-transfer RL (NT). To the best of our knowledge, no existing transfer algorithm is directly comparable to our approach from an experimental perspective. \todo{Any better motivation?}

@@

\begin{figure*}[t]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[trim=1.0cm 0.9cm 1.0cm 0.9cm,clip=true,height=2.5cm]{images/rooms.pdf} \hfill
\includegraphics[trim=0.5cm 0cm 1.8cm 1.3cm,clip=true,height=2.5cm]{images/three-room/lrev.pdf}
\caption{Bla bla bla}
    \label{fig:puddleworld}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/three-room-gen/lrev.pdf} \hfill
\includegraphics[trim=0.5cm 0cm 1.6cm 1.3cm,clip=true,height=2.5cm]{images/likelihood/lrew.pdf}
\caption{Bla bla bla}
    \label{fig:acrobot}
\end{minipage}
\end{figure*}
